---
title: "Covid91 vaccine study Final2022"
author: "Sisilia Martinez!"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "July 26, 2022" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final_Data.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

```{r}
FinalDat <- read.csv(file= "final_Data.csv")
```



# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

# Males
```{r}
Males <- filter(FinalData, sex == "M")
```


## Graphic description
```{r}
dd2 <- Males %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

The bar chart shows the infected rate of Males who took the placebo and those who took the Covid19 vaccine. Looking at the bar chart it shows that out of all the males that got infected with Covid19 more than 70% had taken placebo and about 30% of them took the covid shot. It also shows us that out of the Males that were not infected it is about equal between the group of males who took placebo and who took the Covid19 shot.

## Nummerical Results
```{r}
table1 <- xtabs(~infected + treatment, data=Males)
rowPerc(table1)
colPerc(table1)
```

The numerical results shows us that out of the males that were infected 2.63% of them had taken placebo and 1.28% of them had gotten the Covid19 vaccine. This tells us that the vaccine is effective.

## Inferential Results 
```{r}
chisq.test(table1)
chisqtestGC(table1)
fishtestm <-fisher.test(table1)
print(fishtestm)
```

The inferential results show us that the people who took the placebo were twice as likely to catch Covid then those who took the vaccine. With the p-value being very low it tells us that there is a small chance of getting results like these, if there was no difference between the placebo and Covid19 vaccination. 

## Efficacy
```{r}
options(digits = 1)
maleffic=fishtestm$estimate/(1+fishtestm$estimate)*100
malefficlo=fishtestm$conf.int[1]/(1+fishtestm$conf.int[1])*100
maleffichi=fishtestm$conf.int[2]/(1+fishtestm$conf.int[2])*100
print(maleffic)
print(malefficlo)
print(maleffichi)
```

The confidence interval for the effectiveness of the vaccine on males has low of `r malefficlo` and a high of `r maleffichi`.

# Females
```{r}
Females <-filter(FinalData, sex == "F")
```


## Graphic Description
```{r}
dd2 <- Females %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

The bar chart shows the infected rate of females who took placebo and those who got the Covid19 vaccine. It also shows that out of those who had gotten infected with Covid19, about a little less than 60% of them had taken placebo and about 40% of them had taken the covid shot. Looking at those who did not catch Covid it is about equal between the groups of females who had taken placebo and those who had got the covid shot.

## Nummerical Results 
```{r}
table2 <- xtabs(~infected + treatment, data=Females)
rowPerc(table2)
colPerc(table2)
```

The numerical results show us that out of the females that were infected 2.3% of them had taken placebo and 1.62% of them had gotten the Covid19 vaccine. 


## Inferential Results 
```{r}
chisq.test(table2)
chisqtestGC(table2)
fishtestf <- fisher.test(table2)
fishtestf
```

The inferential results show about 1.43 odds ratio. This tells us that those that took placebo are about 1.43 times as likely to catch covid than those that took the vaccine. The results also gave a low p-value which indicates a low chance of getting these results if there was no difference between females who took the placebo or vaccine. 

## Efficacy
```{r}
femeffic=fishtestf$estimate/(1+fishtestf$estimate)*100
femefficlo=fishtestf$conf.int[1]/(1+fishtestf$conf.int[1])*100
femeffichi=fishtestf$conf.int[2]/(1+fishtestf$conf.int[2])*100
print(femeffic)
print(femefficlo)
print(femeffichi)
```

The confidence interval  for the effectiveness of the vaccine for females has a low of `r femefficlo` and a high of `r femeffichi`.

# LGBTQ
```{r}
LGBTQ <-filter(FinalData, LGBTQ == "gay")
```

## Graphic Description
```{r}
dd2 <- LGBTQ %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

The bar chart shows the infected rate of gays who took the placebo and those who took the covid19 vaccine. Looking at the chart it shows that out of those who had gotten infected with covid19 about 15% of them had taken placebo and a little less than 80% of them had taken the covid19 shot. Looking at those who did not catch covid about 50% of them had taken placebo and a little less than 50% of them had gotten the covid vaccine. 

# Druggies

