---
title: "Covid91 vaccine study Final2022"
author: "Sisilia Martinez!"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "July 26, 2022" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final_Data.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

```{r}
FinalDat <- read.csv(file= "final_Data.csv")
```



# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

# Males
```{r}
Males <- filter(FinalDat, sex == "M")
```

```{r}
Males <- select(Males, -sex)
```

## Graphic description
```{r}
dd2 <- Males %>% group_by(infected,treatment) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=infected,y=count,fill=treatment))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=infected,y=prcnt*100,fill=treatment)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

The bar chart shows the infected rate of Males who took the placebo and those who took the Covid19 vaccine. Looking at th bar chart it shows that out of all the males that got infected with Covid19 more than 70% had taken placebo and about 30% of them took the covid shot. It also shows us that out of the Males that were not infected it is about equal between the group of males who took placebo and who took the Covid19 shot.

## Nummerical Results
```{r}
table1 <- xtabs(~infected + treatment, data=Males)
rowPerc(table1)
colPerc(table1)
```

The numerical results shows us that out of the males that were infected 2.63% of them had taken placebo and 1.28% of them had gotten the Covid19 vaccine. This tells us that the vaccine is effective.

# Females


# LGBTQ



# Druggies

